---
output:
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
header-includes:
- |
  ```{=latex} 
  \usepackage{microtype}
  \usepackage{fontspec}
  \setmainfont{Times.otf}[BoldFont = TimesBold.otf]
  \usepackage{ragged2e}
  \renewcommand{\footnotesize}{\scriptsize \justify}
  \usepackage{setspace}
  \usepackage{xcolor}
  \definecolor{very-light-gray}{gray}{0.95}
  \pagenumbering{gobble}
  \makeatletter
  \def\MT@is@composite#1#2\relax{%
    \ifx\\#2\\\else
      \expandafter\def\expandafter\MT@char\expandafter{\csname\expandafter
                      \string\csname\MT@encoding\endcsname
                      \MT@detokenize@n{#1}-\MT@detokenize@n{#2}\endcsname}%
      % 3 lines added:
      \ifx\UnicodeEncodingName\@undefined\else
        \expandafter\expandafter\expandafter\MT@is@uni@comp\MT@char\iffontchar\else\fi\relax
      \fi
      \expandafter\expandafter\expandafter\MT@is@letter\MT@char\relax\relax
      \ifnum\MT@char@ < \z@
        \ifMT@xunicode
          \edef\MT@char{\MT@exp@two@c\MT@strip@prefix\meaning\MT@char>\relax}%
            \expandafter\MT@exp@two@c\expandafter\MT@is@charx\expandafter
              \MT@char\MT@charxstring\relax\relax\relax\relax\relax
        \fi
      \fi
    \fi
  }
  % new:
  \def\MT@is@uni@comp#1\iffontchar#2\else#3\fi\relax{%
    \ifx\\#2\\\else\edef\MT@char{\iffontchar#2\fi}\fi
  }
  \makeatother
  ```
classoption:
  - landscape
  - a4paper
fontsize: 11pt
geometry: top=1cm, right=1.7cm, bottom=0.6cm, left=1.7cm
urlcolor: blue
params:
  ISO3: NA
  Country: NA
  Country_ISO3: NA
  Continent: NA
  Population: NA
  Density: NA
  GDP: NA
  Antibiotics: NA
  PAG_2030: NA
  Cattle: NA
  Chickens: NA
  Pigs: NA
  resistancebank_surveys: NA
  AMR_Exposure_data_rm: NA
  resistancebank_amr: NA
---

```{r setup, include=FALSE}
# - \setmainfont[Path = \string~/Desktop/, BoldFont =  TimesBold, Extension = .otf]{Times}
# - \setmainfont[ExternalLocation=\string~/, BoldFont =  TimesBold, Extension = .otf]{Times}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.pos = "h",
                      dev = "cairo_pdf")

### Adding minipages in Rmarkdown only seems to work when returned from function
fig_table_verysmall <- function() {
  return("\\begin{minipage}{0.30\\textwidth}")
}

fig_table_small <- function() {
  return("\\begin{minipage}{0.33\\textwidth}")
}

fig_table_large <- function() {
  return("\\begin{minipage}{0.67\\textwidth}")
}

fig_table_verylarge <- function() {
  return("\\begin{minipage}{0.70\\textwidth}")
}

fig_table_end <- function() {
  return("\\end{minipage}")
}
```

\setstretch{1}

\begin{center}
\LARGE\textbf{Antimicrobial resistance in animals in `r params[["Country"]]`}\\
\normalsize\href{https://resistancebank.org}{resistancebank.org}
\end{center}

`r fig_table_small()`

```{r P50 map, out.width="248pt", out.height="186pt"}
selected_country <- params[["Country"]]

download.file(url = paste0(paste0("https://amr-hegep-bucket.s3.eu-central-1.amazonaws.com/downloads/",
                                  version,
                                  "/country_reports/other_plots/P50_rasters/"),
                    gsub(pattern = " ",
                         replacement = "+",
                         x = selected_country),
                    ".png"),
          destfile = paste0(tempdir(),
                            gsub(pattern = " ",
                                 replacement = "+",
                                 x = selected_country),
                            ".png"),
          mode = 'wb')

knitr::include_graphics(path = paste0(tempdir(),
                                      gsub(x = selected_country,
                                           pattern = " ",
                                           replacement = "+"),
                                      ".png"))
```

\vspace{2pt}

\setstretch{0.3}

\begingroup\scriptsize
\textbf{Figure 1}. Hotspots. Percentage of antimicrobial drugs with resistance higher than 50\%, \href{https://science.sciencemag.org/content/365/6459/eaaw1944?fbclid=IwAR28EBh4FvZXyrDmaIFCFcLdK_8yyku0AFfjUUbDvkn-S9OwEisEXA7S1zo}{Van Boeckel \& Pires, Global Trends in Antimicrobial Resistance in Animals in Low- and Middle-Income Countries, Science 365, (2019)}.
\endgroup

\setstretch{1}

\vspace{4pt}

```{r piecharts, fig.align='center', fig.height=3}
resistancebank_surveys <- params[["resistancebank_surveys"]]

resistancebank_surveys$Study <- 1

years <- data.frame("DOI" = "nostudy",
                    "PubDate" = as.character(seq(from = 2000,
                                                 to = max(x = as.integer(unique(resistancebank_surveys$PubDate)),
                                                          na.rm = TRUE),
                                                 by = 1)),
                    "Study" = 0)

for (i in names(resistancebank_surveys)[!names(resistancebank_surveys) %in% c("DOI", "PubDate", "Study")]) {
  
  years[, i] <- NA
  
}

resistancebank_surveys <- rbind(resistancebank_surveys,
                                years[!years$PubDate %in% resistancebank_surveys$PubDate, ])

resistancebank_surveys <- resistancebank_surveys[order(resistancebank_surveys$PubDate,
                                                       decreasing = FALSE), ]

my_breaks <- seq(from = "2000",
                 to = max(as.character(years$PubDate)),
                 by = 1)

resistancebank_surveys$Type <- sapply(X = 1:nrow(resistancebank_surveys),
                                      FUN = function(i) {
                                        
                                        if (is.na(resistancebank_surveys$Journal[i])) {
                                          
                                          return(NA)
                                          
                                        } else if (resistancebank_surveys$Journal[i] == 
                                            "Report could not be linked to a peer-reviewed publication.") {
                                          
                                          as.character("Gray literature") 
                                          
                                        } else {
                                          
                                          as.character("Peer-reviewed")
                                          
                                        }
                                        
                                      })

if (length(unique(na.omit(resistancebank_surveys$Type))) == 2) {
  
  resistancebank_surveys$Type <- factor(x = resistancebank_surveys$Type,
                                        levels = c("Gray literature",
                                                   "Peer-reviewed"))
  
}

country_data <- data.frame("Variable" = c("Population",
                                          "GDP",
                                          "Peer-reviewed",
                                          "Gray literature",
                                          "Cattle",
                                          "Chickens",
                                          "Pigs",
                                          "Antibiotics",
                                          "PAG_2030"),
                           "Value" = c(params[["Population"]],
                                       params[["GDP"]],
                                       sum(subset(x = resistancebank_surveys,
                                                  subset = !is.element(el = DOI,
                                                                       set = "nostudy"))$Type == "Peer-reviewed"),
                                       sum(subset(x = resistancebank_surveys,
                                                  subset = !is.element(el = DOI,
                                                                       set = "nostudy"))$Type == "Gray literature"), # No Gray literature = sum will be 0, fine for plotting
                                       params[["Cattle"]],
                                       params[["Chickens"]],
                                       params[["Pigs"]],
                                       params[["Antibiotics"]],
                                       params[["PAG_2030"]]))

###= Antimicrobial usage =#####
au_piechart <- ggplot(data = country_data[1, ], # I've used the "Population" data because it's never 0 and hence the one-colour pie chart is displayed
       aes(x = "",
           y = Value)) +
  geom_bar(stat = "identity",
           width = 1,
           fill = "lightblue") +
  coord_polar(theta = "y",
              start = 0) +
  labs(title = expression(paste(bold(Antimicrobial),
                                " ",
                                bold(use^1)))) +
  geom_text(label = paste(ifelse(test = is.na(country_data$Value[8]),
                                  yes = "---",
                                  no = paste0(format(x = country_data$Value[8],
                                                     big.mark = ","),
                                              " tonnes/y")),
                          ifelse(test = is.na(country_data$Value[9]),
                                 yes = "---",
                                 no = paste0(ifelse(test = country_data$Value[9] >= 0, yes = "+", no = ""), country_data$Value[9], "% in 2030")),
                          " ",
                          " ",
                          sep = "\n"),
            size = 4.7,
            family = "Times",
            position = position_stack(vjust = 0.5)) +
  theme_void() +
  theme(text = element_text(family = "Times"),
        plot.title = element_text(size = 14,
                                  face = "bold",
                                  hjust = 0.5),
        legend.position = "none")

###= Livestock =#####
livestock_data <- na.omit(country_data[5:7, ])

livestock_data$Rounded <- sapply(X = 1:nrow(livestock_data),
                                 FUN = function(i) {
                                   
                                   if (livestock_data$Value[i] >= 1e9) {
                                     
                                     paste(format(round(x = livestock_data$Value[i]/1e9,
                                                          digits = 2),
                                                    big.mark = ",",
                                                    trim = TRUE),
                                             "B",
                                             sep = "")
                                     
                                   } else if (livestock_data$Value[i] >= 1e6) {
                                     
                                     paste(format(round(x = livestock_data$Value[i]/1e6,
                                                          digits = 2),
                                                    big.mark = ",",
                                                    trim = TRUE),
                                             "M",
                                             sep = "")
                                     
                                   } else if (livestock_data$Value[i] >= 1e3 &
                                              livestock_data$Value[i] < 1e6) {
                                     
                                     paste(format(round(x = livestock_data$Value[i]/1e3,
                                                          digits = 2),
                                                    big.mark = ",",
                                                    trim = TRUE),
                                             "K",
                                             sep = "")
                                     
                                   } else {
                                     
                                     format(round(x = livestock_data$Value[i],
                                                  digits = 2),
                                            trim = TRUE)
                                     
                                   }
                                   
                                 })

livestock_piechart <- ggplot(data = livestock_data,
       aes(x = "",
           y = Value,
           fill = Variable)) +
  geom_bar(stat = "identity",
           width = 1) +
  coord_polar(theta = "y",
              start = 0) +
  scale_fill_manual(values = c("Cattle" = "#83C77A",
                               "Chickens" = "#F9A600",
                               "Pigs" = "#F5C0CD")[c(unique(livestock_data$Variable))],
                    labels = c(unique(livestock_data$Variable))) +
  labs(title = expression(paste(bold(Livestock), " ", bold(heads^2)))) +
  theme_void() +
  ggrepel::geom_text_repel(aes(label = Rounded),
                           size = 4.7,
                           family = "Times",
                           position = position_stack(vjust = 0.5)) +
  theme_void() +
  theme(text = element_text(family = "Times"),
        plot.title = element_text(size = 14,
                                  face = "bold",
                                  hjust = 0.5),
        legend.position = c(0.5, -0.05),
        legend.box = "vertical",
        legend.direction = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size = 13),
        legend.margin = margin(0, 0, 0, 0),
        legend.box.margin = margin(0, 0, 0, 0),
        legend.key.size = unit(0.6, "cm")) +
  guides(fill = guide_legend(ncol = 2))

###= Population & GDP =#####
population_piechart <- ggplot(data = country_data[1, ],
       aes(x = "",
           y = Value)) +
  geom_bar(stat = "identity",
           width = 1,
           fill = "grey85") +
  coord_polar(theta = "y",
              start = 0) +
  labs(title = expression(paste(bold(Population^3), ", ", bold(GDP^4)))) +
  geom_text(label = paste(paste(ifelse(test = country_data$Value[1] >= 1e9,
                                       yes = paste(format(round(x = country_data$Value[1]/1e9,
                                                               digits = 1),
                                                               trim = TRUE),
                                                        "B",
                                                        sep = ""),
                                       no = ifelse(test = country_data$Value[1] < 1e9 & country_data$Value[1] >= 1e6,
                                                   yes = paste(format(round(x = country_data$Value[1]/1e6,
                                                                            digits = 1),
                                                                      trim = TRUE),
                                                        "M",
                                                        sep = ""),
                                                   no = ifelse(test = country_data$Value[1] < 1e6 & country_data$Value[1] >= 1e3,
                                                               yes = paste(format(round(x = country_data$Value[1]/1e3,
                                                                                        digits = 1),
                                                                                  trim = TRUE),
                                                                           "K",
                                                                           sep = ""),
                                                               no = country_data$Value[1]))),
                                     " inhab.",
                                     sep = ""),
                          ifelse(test = is.na(country_data$Value[2]),
                                 yes = paste0("---"),
                                 no = ifelse(test = country_data$Value[2] >= 1e3,
                                             yes = paste(format(round(x = country_data$Value[2]/1e3,
                                                                      digits = 1),
                                                                trim = TRUE),
                                                         "K USD/in.",
                                                         sep = ""),
                                             no = paste(country_data$Value[2],
                                                        "USD/in."))),
                          " ",
                          " ",
                          sep = "\n"),
            size = 4.7,
            family = "Times",
            position = position_stack(vjust = 0.5)) +
  theme_void() +
  theme(text = element_text(family = "Times"),
        plot.title = element_text(size = 14,
                                  face = "bold",
                                  hjust = 0.5),
        legend.position = "none")

###= Studies and gray literature =#####
sgl_piechart <- ggplot(data = {if (sum(subset(x = resistancebank_surveys,
                                                  subset = !is.element(el = DOI,
                                                                       set = "nostudy"))$Type == "Gray literature") != 0) {country_data[3:4, ]} else {country_data[3, ]}},
       aes(x = "",
           y = Value,
           fill = Variable)) +
  geom_bar(stat = "identity",
           width = 1) +
  geom_text(aes(label = Value),
            size = 4.7,
            family = "Times",
            position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values = c("Gray literature" = "#FF6C67",
                               "Peer-reviewed" = "#00C2C6")) +
  coord_polar(theta = "y",
              start = 0) +
  labs(title = expression(bold("Surveys"))) +
  theme_void() +
  theme(text = element_text(family = "Times"),
        plot.title = element_text(size = 14,
                                  face = "bold",
                                  hjust = 0.5),
        legend.position = c(0.5, -0.05),
        legend.box = "vertical",
        legend.direction = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size = 13),
        legend.margin = margin(0, 0, 0, 0),
        legend.box.margin = margin(0, 0, 0, 0),
        legend.key.size = unit(0.6, "cm"))

###= 4 piecharts combination
gridExtra::grid.arrange(au_piechart,
                        livestock_piechart,
                        population_piechart,
                        sgl_piechart,
                        nrow = 1)
```

\vspace{4pt}

```{r, fig.align='center', fig.height=2.9}
# Barplot of the studies per year
ggplot(data = resistancebank_surveys,
       aes(x = as.factor(PubDate),
           y = Study,
           fill = Type)) +
  stat_summary(fun = sum,
               geom = "bar",
               position = "stack") + 
  geom_hline(yintercept = sum(resistancebank_surveys$Study)/length(my_breaks),
             linetype = "dashed",
             colour = "red",
             size = 0.8) +
    scale_fill_manual(values = c("Gray literature" = "#FF6C67",
                                 "Peer-reviewed" = "#00C2C6")[c(unique(na.omit(resistancebank_surveys$Type)))]) +
    scale_x_discrete(breaks = my_breaks,
                     labels = label_fill(orig = my_breaks,
                                         .mod = 6)) +
    scale_y_continuous(breaks = function(x) unique(floor(pretty(x)))) +
    labs(x = "Year",
         y = "Surveys") +
    theme(text = element_text(family = "Times"),
          axis.title = element_text(size = 14,
                                    face = "bold"),
          axis.text = element_text(colour = "black",
                                   size = 14),
          plot.margin = margin(t = 0.3,
                               r = 0.3,
                               b = 0.3,
                               l = 0.3,
                               unit = "cm"),
          panel.background = element_rect(fill = "white"),
          panel.grid = element_line(colour = "gray93"),
          legend.position = "none")
```

\vspace{2pt}

\setstretch{0.3}

\begingroup\scriptsize
\textbf{Figure 2}. Number of peer-reviewed surveys{`r if (sum(subset(x = resistancebank_surveys, subset = !is.element(el = DOI, set = "nostudy"))$Type == "Gray literature") != 0) {" and gray literature reports,"} else {""}`} and average number of point-prevalence surveys per year (red line).
\endgroup

`r fig_table_end()`
`r fig_table_large()`

\setstretch{0.3}

\vspace{2pt}

```{r, fig.align='right', fig.height=3.6, fig.width=6.7}
country_exposure_images_report <- country_exposure_images

country_exposure_images_report$Country <- c("Senegal",
                                            "Rwanda",
                                            "Burkina Faso")

country_exposure_images_report[1, 2] <- 0.50
country_exposure_images_report[3, 2] <- 0.41
country_exposure_images_report[3, 5] <- 0.10

if (params[["ISO3"]] %in% params[["AMR_Exposure_data_rm"]]$ISO3) {

  ggplot(data = params[["AMR_Exposure_data_rm"]],
         aes(x = reorder_within(Country, desc(Exposure), Animal_species),
             y = Exposure)) +
    geom_col(aes(fill = Continent),
             colour = "black",
             size = 0.1) +
    ggimage::geom_image(data = country_exposure_images_report,
                        image = country_exposure_images_report$image,
                        size = country_exposure_images_report$Size - 0.043,
                        asp = country_exposure_images_report$Aspect_ratio + 5.4) +
    lemon::facet_rep_wrap(~Animal_species,
                          scales = "free",
                          repeat.tick.labels = "all",
                          nrow = 3) +
    scale_fill_manual(values = c("orange",
                                 "red",
                                 "black")) +
    scale_y_continuous(breaks = seq(from = 0,
                                    to = 0.5,
                                    by = 0.2)) +
    scale_x_reordered() +
    labs(x = NULL,
         y = expression(paste(bold("National P50 level "), "[", bold("%"), "]")),
         fill = NULL) +
    theme(text = element_text(family = "Times"),
          axis.text.x = element_text(colour = "black",
                                     size = 4.1,
                                     angle = 90,
                                     hjust = 1),
          axis.title.y = element_text(size = 7.5),
          axis.text.y = element_text(colour = "black",
                                     size = 7.5),
          axis.ticks.length = unit(0.05, "cm"),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_line(size = 0.2),
          panel.background = element_blank(),
          panel.spacing = unit(0, "lines"),
          strip.text.x = element_blank(),
          strip.background = element_blank(),
          legend.text = element_text(size = 7.5),
          legend.box = "horizontal",
          legend.direction = "horizontal",
          legend.position = c(0.5, 0.97),
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(0, 0, 0, 0),
          legend.key.size = unit(0.3, "cm"),
          legend.spacing.x = unit(0.1, "cm")) +
    geom_segment(aes(x = reorder_within(Country, desc(Exposure), Animal_species),
                     xend = reorder_within(Country, desc(Exposure), Animal_species),
                     y = Exposure + 0.14,
                     yend = Exposure + 0.015,
                     color = Selection,
                     alpha = Selection),
                 size = 0.6,
                 arrow = arrow(length = unit(1, "mm"),
                               type = "closed"),
                 show.legend = FALSE) +
    scale_color_manual(values = c("TRUE" = "black",
                                  "FALSE" = "white")) +
    scale_alpha_manual(values = c("TRUE" = 1,
                                  "FALSE" = 0))

}

# ggsave(filename = paste0(tempdir(), "/plot_nico.png"),
#        plot = a)
# 
# put_object(file = paste0(tempdir(), "/plot_nico.png"),
#              object = "plot_nico.png",
#              bucket = "amr-hegep-bucket",
#              acl = c("public-read"))
```

```{r, fig.align='right', out.height="297pt", out.width="475.2pt"}
if (!(params[["ISO3"]] %in% params[["AMR_Exposure_data_rm"]]$ISO3)) {
  
  download.file(url = paste0("https://amr-hegep-bucket.s3.eu-central-1.amazonaws.com/downloads/",
                             version,
                             "/country_reports/other_plots/amr_exposure_plot_report_transparent.png"),
                destfile = paste0(tempdir(),
                                  "amr_exposure_plot_report_transparent.png"),
                mode = 'wb')

  knitr::include_graphics(path = paste0(tempdir(),
                                        "amr_exposure_plot_report_transparent.png"))
  
}
```

\vspace{2pt}

\setlength{\leftskip}{1cm}

\begingroup\scriptsize
\textbf{Figure 3}. Relative country-level exposure to antimicrobial resistance in chickens, pigs and cattle. This metric quantifies the exposure levels of the animal populations. The analysis was restricted to countries with at least 10 million chicken, 250,000 pigs, and 500,000 cattle heads.
\endgroup

\vspace{18pt}

```{r, fig.align='right', fig.height=2.3, fig.width=6.7}
resistancebank_amr <- params[["resistancebank_amr"]]

if (nrow(resistancebank_amr) > 0) {
  
  resistancebank_amr_list <- split(x = resistancebank_amr,
                                   f = list(resistancebank_amr$Author,
                                            resistancebank_amr$DOI,
                                            resistancebank_amr$YCoord,
                                            resistancebank_amr$XCoord,
                                            resistancebank_amr$PubDate),
                                   drop = TRUE,
                                   lex.order = TRUE)

  resistancebank_amr_pathogens <- NULL
  
  for (i in 1:length(resistancebank_amr_list)) {
    
    resistancebank_amr_pathogens <- c(resistancebank_amr_pathogens, 
                                      as.character(unique(resistancebank_amr_list[[i]][["Pathogens"]])))
    
  }

  # Number of surveys per pathogen
  named_resistancebank_amr_pathogens <- c(table(resistancebank_amr_pathogens))
  
  # Number of isolates per pathogen
  resistancebank_amr_isolates <- resistancebank_amr %>% 
    dplyr::distinct(Author, DOI, YCoord, XCoord, PubDate, ISO3, Species, Pathogens, NIsolates) %>% 
    dplyr::group_by(Pathogens) %>% 
    dplyr::summarise(Isolates = sum(NIsolates, na.rm = T))
  
  facets_resistancebank_amr_names <- NULL

  # Facets text
  for (i in names(named_resistancebank_amr_pathogens)) {

    facets_resistancebank_amr_names <- c(facets_resistancebank_amr_names,
                                         bquote(bold(.(names(named_resistancebank_amr_pathogens)[which(names(named_resistancebank_amr_pathogens) == i)])) ~
                                                bold("("*n[s]*" =" ~ bold(.(format(named_resistancebank_amr_pathogens[[i]],
                                                                                   big.mark = ",")))*"," ~
                                                bold(n[i]*" =" ~ bold(.(format(resistancebank_amr_isolates$Isolates[resistancebank_amr_isolates$Pathogens == i],
                                                                               big.mark = ",")))*")"))))

  }

  resistancebank_amr$Pathogens <- factor(resistancebank_amr$Pathogens,
                                         labels = facets_resistancebank_amr_names)

  # Barplot
  resistancebank_amr_plot <- ggplot(data = resistancebank_amr,
         aes(x = reorder_within(Compound,
                                desc(Rescom),
                                Pathogens),
             y = Rescom,
             fill = Species)) +
    stat_summary(geom = "bar",
                 fun = mean,
                 position = position_dodge(preserve = "single"),
                 colour = "black",
                 size = 0.1,
                 width = {if (length(unique(resistancebank_amr$Compound)) <= 9 &
                              length(unique(resistancebank_amr$Pathogens)) == 1) {0.2}}) +
    stat_summary(geom = "errorbar",
                 fun.data = mean_se,
                 position = position_dodge(preserve = "single",
                                           width = 0.9),
                 width = ifelse(test = length(unique(resistancebank_amr$Compound)) <= 9 &
                                       length(unique(resistancebank_amr$Pathogens)) == 1,
                                yes = 0.1,
                                no = 0.4),
                 size = 0.1) +
    scale_y_continuous(breaks = c(0, 50, 100),
                       limits = c(0, 100)) +
    scale_fill_manual(values = c("Buffalo" = "#F9766D",
                                 "Cattle" = "#83C77A",
                                 "Camel" = "#B8860B",
                                 "Chicken" = "#F9A600",
                                 "Duck" = "#00BFC4",
                                 "Goat" = "#016400",
                                 "Horse" = "#C77CFF",
                                 "Pig" = "#F5C0CD",
                                 "Rabbit" = "#FFDEAD",
                                 "Sheep" = "#BFBFBF",
                                 "Turkey" = "#1A74CD")[c(unique(as.character(resistancebank_amr$Species)))]) +
    scale_x_reordered() +
    facet_wrap(facets = ~Pathogens,
               scales = "free_x",
               labeller = label_parsed) +
    labs(x = NULL,
         y = expression(paste(bold("Resistance "), "[", bold("%"), "]"))) +
    theme(text = element_text(family = "Times"),
          axis.title = element_text(size = 7.5),
          axis.title.x = element_text(face = "bold"),
          axis.text.x = element_text(size = 5,
                                     colour = "black",
                                     angle = 90,
                                     hjust = 1),
          axis.text.y = element_text(colour = "black",
                                       size = 7.5),
          axis.ticks = element_line(size = 0.2),
          axis.ticks.length = unit(0.05, "cm"),
          strip.text.x = element_text(size = 7.5,
                                      face = "bold"),
          strip.background.x = element_rect(fill = "white"), 
          panel.background = element_rect(fill = "white"),
          panel.grid.major.x = element_blank(),
          panel.grid.major.y = element_line(colour = "lightgray",
                                            size = 0.1),
          legend.text = element_text(size = 6.4),
          legend.title = element_blank(),
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(0, 0, 0, 0),
          legend.key.size = unit(0.20, "cm"),
          legend.spacing.x = unit(0.1, 'cm'),
          legend.background = element_rect(color = NA))
  
  if (length(unique(resistancebank_amr$Pathogens)) == 1 |
      length(unique(resistancebank_amr$Pathogens)) == 2) {
  
    resistancebank_amr_plot <- resistancebank_amr_plot +
      theme(legend.box = "horizontal",
            legend.direction = "horizontal",
            legend.position = c(ifelse(test = length(unique(resistancebank_amr$Pathogens)) == 1 & 
                                              length(unique(resistancebank_amr$Species)) == 4,
                                       yes = 0.1,
                                       no = ifelse(test = length(unique(resistancebank_amr$Pathogens)) == 1 & 
                                                          length(unique(resistancebank_amr$Species)) == 3,
                                                   yes = 0.07,
                                                   no = ifelse(test = length(unique(resistancebank_amr$Pathogens)) == 1 & 
                                                                      length(unique(resistancebank_amr$Species)) == 2,
                                                               yes = 0.05,
                                                               no = ifelse(test = length(unique(resistancebank_amr$Pathogens)) == 1 & 
                                                                                  length(unique(resistancebank_amr$Species)) == 1,
                                                                           yes = 0.032,
                                                                           no = 0.5)))),
                                1.08))
    
  } else if (length(unique(resistancebank_amr$Pathogens)) == 3) {
    
    resistancebank_amr_plot <- resistancebank_amr_plot +
      theme(legend.key = element_rect(fill = NA,
                                      colour = "black",
                                      size = 0.1),
            legend.position = c(0.95, 0.87))
    
  } else if (length(unique(resistancebank_amr$Pathogens)) == 4) {
    
    resistancebank_amr_plot <- resistancebank_amr_plot +
      theme(legend.key = element_rect(fill = NA,
                                      colour = "black",
                                      size = 0.1),
            legend.position = c(0.97, 0.99))
    
  }
  
  resistancebank_amr_plot

}
```

```{r, fig.align='right', out.height="294pt", out.width="470.4pt"}
if (nrow(resistancebank_amr) == 0) {
  
  download.file(url = paste0("https://amr-hegep-bucket.s3.eu-central-1.amazonaws.com/downloads/",
                             version,
                             "/country_reports/other_plots/plot_AGISAR_transparent.png"),
                destfile = paste0(tempdir(),
                                  "plot_AGISAR_transparent.png"),
                mode = 'wb')

  knitr::include_graphics(path = paste0(tempdir(),
                                        "plot_AGISAR_transparent.png"))
  
}
```

```{r, results="asis"}
# Function to add link 
myFun <- function(text, link, inline=TRUE) {
  if(inline) {
    paste("[", text, "](", link, ")", sep="")
  } else {
    cat("[", text, "](", link, ")", sep="")
  }
}
```

\vspace{2pt}

\begingroup\scriptsize
\textbf{Figure 4}. Resistance rates, number of surveys (n$_{s}$) and total number of isolates tested (n$_{i}$) by pathogen listed by the \href{https://www.who.int/foodsafety/areas_work/antimicrobial-resistance/agisar/en/}{AGISAR consortium}. See protocol S1 in \href{https://science.sciencemag.org/content/sci/suppl/2019/09/18/365.6459.eaaw1944.DC1/aaw1944-Van-Boeckel-SM.pdf}{Van Boeckel \& Pires, Science 365, (2019)}.
\endgroup

`r fig_table_end()`

\setstretch{0.3}

`r fig_table_verylarge()`

\begingroup\scriptsize
\rule[2pt]{7cm}{0.3pt}\\
$^1$Data updated to 2020. Source: Mulchandani et al., Global trends in antimicrobial use in food-producing animals: 2020 to 2030 (Accepted).\\
$^2$Data updated to 2022. Source: \href{http://www.fao.org/faostat/en/\#data/QA}{FAOSTAT}.\\
$^3$Data updated to 2018. Source: \href{http://wdi.worldbank.org}{World Development Indicators}.\\  
$^4$Data updated to 2016. Source: \href{https://data.worldbank.org/indicator/ny.gdp.mktp.cd}{World Bank Group}.\\
\endgroup

`r fig_table_end()`
`r fig_table_verysmall()`

\fcolorbox{black}{very-light-gray}{\begin{minipage}{21em}
\begingroup\footnotesize
\begin{center}
\textbf{Disclaimer}\\
\end{center}
\endgroup
\rule[2pt]{7.8cm}{0.3pt}\\
\begingroup\tiny
The information in this country-report result from the aggregation, and extrapolation of data from surveys conducted by independent scientists. It does not reflect the official positions of {`r if (params[["Continent"]] == "Europe") {paste("the ", "\\href{https://www.efsa.europa.eu/en/efsajournal/pub/7209}{European Food Safety Authority}", " and")} else {""}`} the country’s veterinary authorities on antimicrobial resistance levels in animals in {`r params[["Country"]]`}. The detailed methodology and data source for this country-report are presented in \href{https://science.sciencemag.org/content/365/6459/eaaw1944?fbclid=IwAR28EBh4FvZXyrDmaIFCFcLdK_8yyku0AFfjUUbDvkn-S9OwEisEXA7S1zo}{Van Boeckel \& Pires, 2019}.
\endgroup
\end{minipage}}

`r fig_table_end()`
